A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-06 project/PaperTemplate/paper.Rmd
Redid simulation

```{r, cache = TRUE}
set.seed(495)
sim_reps <- 10000

@@

```{r}
library(boot)

mean.fun <- function(d, i) {
  d <- X[i]
  return (c(mean(d), sd(d)))
}

@@

  sim_reps <- 10000
  norm_contains <- rep(0, sim_reps)
  basic_contains <- rep(0, sim_reps)
  student_contains <- rep(0, sim_reps)
  percentile_contains <- rep(0, sim_reps)
  bca_contains <- rep(0, sim_reps)

@@

  set.seed(495)
  for (j in 1:sim_reps) {
    X <- rlnorm(n, 0, 1)
    values <- data.frame(X)

@@

    norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
    basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    student_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    percentile_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
    bca_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]

@@

  master[i, 1] <- sample_sizes[i]
  master[i, 2] <- sum(norm_contains)/sim_reps
  master[i, 3] <- sum(basic_contains)/sim_reps
  master[i, 4] <- sum(student_contains)/sim_reps
  master[i, 5] <- sum(percentile_contains)/sim_reps
  master[i, 6] <- sum(bca_contains)/sim_reps

@@

@@

>>>>

```{r, cache = TRUE, eval = FALSE}
set.seed(495)
sim_reps <- 10000

@@

```{r, warning = FALSE}
library(boot)

run_sim_log_normal <- function(sim_reps) {
  set.seed(495)
  mean.fun <- function(d, i) {
    d <- X[i]
    return (c(mean(d), sd(d)))
  }

@@

    norm_contains <- rep(0, sim_reps)
    basic_contains <- rep(0, sim_reps)
    student_contains <- rep(0, sim_reps)
    percentile_contains <- rep(0, sim_reps)
    bca_contains <- rep(0, sim_reps)

@@

    for (j in 1:sim_reps) {
      X <- rlnorm(n, 0, 1)
      values <- data.frame(X)

@@

      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]

@@

    master[i, 1] <- sample_sizes[i]
    master[i, 2] <- sum(norm_contains)/sim_reps
    master[i, 3] <- sum(basic_contains)/sim_reps
    master[i, 4] <- sum(student_contains)/sim_reps
    master[i, 5] <- sum(percentile_contains)/sim_reps
    master[i, 6] <- sum(bca_contains)/sim_reps
  }

  master_df <- as.data.frame(master) %>% 
      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
             "Percentile" = V5, "BCa" = V6) 
  master_df
}
```

```{r}
master_df_long <- master_df %>%
  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

master_fig <- ggplot(data = master_df_long, 
                    aes(x = Sample_Size, y = prop, color = method)) + 
  geom_point() + geom_line() + 
  labs(title = "Proportion of CIs that Contain the True Parameter from Log-Normal
       Distibution", x = "Sample Size", 
       y = "Proportion (of 10,000 Simulations)", color = "Method",
       caption = "Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for different sample sizes on Log-Normal Dist.") +
  theme_light() +
  theme(legend.position="bottom")

master_fig
```
```{r, warning = FALSE}
library(boot)

run_sim_normal <- function(sim_reps) {
  set.seed(495)
  mean.fun <- function(d, i) {
    d <- X[i]
    return (c(mean(d), sd(d)))
  }

    norm_contains <- rep(0, sim_reps)
    basic_contains <- rep(0, sim_reps)
    student_contains <- rep(0, sim_reps)
    percentile_contains <- rep(0, sim_reps)
    bca_contains <- rep(0, sim_reps)

    boot_reps <- 2000
    n <- sample_sizes[i]
    true_mean <- 0

    for (j in 1:sim_reps) {
      X <- rnorm(n, 0, 1)
      values <- data.frame(X)

      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]

@@

    master[i, 1] <- sample_sizes[i]
    master[i, 2] <- sum(norm_contains)/sim_reps
    master[i, 3] <- sum(basic_contains)/sim_reps
    master[i, 4] <- sum(student_contains)/sim_reps
    master[i, 5] <- sum(percentile_contains)/sim_reps
    master[i, 6] <- sum(bca_contains)/sim_reps
  }

  master_df <- as.data.frame(master) %>% 
      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
             "Percentile" = V5, "BCa" = V6) 
  master_df
}

@@

```{r, warning = FALSE}
library(boot)

run_sim_gamma <- function(sim_reps) {
  set.seed(495)
  mean.fun <- function(d, i) {
    d <- X[i]
    return (c(mean(d), sd(d)))
  }

    norm_contains <- rep(0, sim_reps)
    basic_contains <- rep(0, sim_reps)
    student_contains <- rep(0, sim_reps)
    percentile_contains <- rep(0, sim_reps)
    bca_contains <- rep(0, sim_reps)

    boot_reps <- 2000
    n <- sample_sizes[i]
    true_mean <- 4

    for (j in 1:sim_reps) {
      X <- rgamma(sample_sizes, shape = 1, scale = 4)
      values <- data.frame(X)

      norm_contains[j] <- true_mean >= ci$normal[2] & true_mean <= ci$normal[3]
      basic_contains[j] <- true_mean >= ci$basic[4] & true_mean <= ci$basic[5]
      student_contains[j] <- true_mean >= ci$student[4] & true_mean <= ci$student[5]
      percentile_contains[j] <- true_mean >= ci$percent[4] & true_mean <= ci$percent[5]
      bca_contains[j] <- true_mean >= ci$bca[4] & true_mean <= ci$bca[5]

    master[i, 1] <- sample_sizes[i]
    master[i, 2] <- sum(norm_contains)/sim_reps
    master[i, 3] <- sum(basic_contains)/sim_reps
    master[i, 4] <- sum(student_contains)/sim_reps
    master[i, 5] <- sum(percentile_contains)/sim_reps
    master[i, 6] <- sum(bca_contains)/sim_reps
  }

  master_df <- as.data.frame(master) %>% 
      rename("Sample_Size" = V1, "Normal" = V2, "Basic" = V3, "Studentized" = V4, 
             "Percentile" = V5, "BCa" = V6) 
  master_df
}

```{r}
set.seed(495)
log_normal_df <- run_sim_log_normal(10000)
write.csv(log_normal_df,"log_normal_df.csv", row.names = FALSE)

normal_df <- run_sim_normal(10000)
write.csv(normal_df,"normal_data_df.csv", row.names = FALSE)

gamma_df <- run_sim_gamma(10000)
write.csv(gamma_df,"gamma_data_df.csv", row.names = FALSE)
